\begin{center}
ACKNOWLEDGMENTS
\end{center}
\setstretch{1.25}


I would like to thank several sources of funding I recieved throughout graduate school.
The William Webber Voyager Graduate Fellowship provided a welcome financial relief during the first two semesters that was especially important before the Graduate Workers Union wins to substantially increase salaries and tuition remission from the Graduate School for graduate workers.
I was also supported by teaching assitantships for three semesters, which provided some of the most hubling experiences during my time at New Mexico State University.
I was supported for three years by the National Science Foundation under grant NSF AST-2206096 which was awarded to release a public, open-source Monte Carlo simulation code for the community to simulate and test the sources from active galactic nuclei for LIGO/Virgo/Kagra gravitational wave detectors.
I also received a small amount of funding from several Department of Astronomy awards, namely the Pegasus Award, Rappaport Award, and Zia Award, and the Graduate school Outstanding Graduate Assistant Award.
Finally, my last semester was supported by the NMSU Spring Semester Graduate Assistantship Award.

First and foremost, I want to thank and acknowledge my advisor Dr. Wladimir Lyra. Wlad, I am so appreciative for all that you've done for me.
From the start, you took me on as your first Ph.D. student even though I said I was interested in AGN and galaxies not planets.
After asking around, you were able to connect me with the AGN channel folks in New York and we embarked on a quick project to blow up a star in a disk that would only take seven years!
On top of that, you nominated me for awards and scholarships practically looking under every planetessimal, pebble, and dust grain to find funding for me and my decidedly NOT planets research, though maybe there ARE planets in AGN disks.
I'm also grateful for your support beyond the research.
It got tough there for a while, and I'm uncertain I would have made it through without some of our breakfasts.
Also, a huge thanks to you and Adirenne for hosting all the incredible Brazillian barbeques and dinner parties.

I would also like to express thanks to my committee for their part in getting me here.
Dr. Moire Prescott, thanks for all of observational contex that built my intution for galaxies and AGN in the Galaxies I class.
I'll always remember when I mentioned in passing to Dr. Kristian Finlator that I had managed to successfully compile my supernova model on the Stampede 2 high performance computer using multiple nodes for the first time.
Your simple "Congratulations! That's a great accomplishment." was unexpected and baffled me in the moment, since at the time it felt I had just done the barest of minimums, but it was most welcome and a compliment I didn't realize I needed to hear.
Dr. Michael Engelhardt, the general relativity will likey finally come in hand in the next phases of this work.

None of this work would have been possible without the hundreds (thousands?) of meetings with collaborators and research groups throughout the years.
Dr. Mordecai Mark Mac Low, thanks for watching me live code and debug through video calls.
Your guidance was instrumental in kickstarting my hydrodynamics research and keeping me organized.
to Saavik, Barry, and the McFAM

more coming...
%TIDYNYC
%Ana Gabela

%Tons of people I met at conferences.

%MVSAR

%Issiah Araceli

%Marines

%My many office mates

%Q continuum

%Ali

%Ezra

%Priscilla

%Unca Bob

%Anna

%Garrett

%Mom \& Dad

%Mitch \& Madison

%Pluto

%Massi

%Funding
